\documentclass[12pt]{amsart}
\usepackage{amsmath,cmap,amssymb}
\begin{document}

\section{Introduction}
\label{sec:intro}

Then $\delta$ is a congruence relation. I can type formulas!

A source file is made up of text, formulas (e.g.,$\sqrt{5}$), and \emph{instructions to} \LaTeX (\TeX).

\section{Some subtle differences}
\label{sec:diffs}
\begin{enumerate}
\item My first integral: $\int \zeta^{2}(x) \, dx$. (with \verb"\,") % \, създава полуинтервал

\item My first integral: $\int \zeta^{2}(x) \ dx$. (with \verb"\ ") % \ създава друг вид интервал

\item My first integral: $\int \zeta^{2}(x) dx$. (with \verb"  ") % просто интервал

\end{enumerate}

FORTRAN. New \dots

FORTRAN\@. New \dots

fortran. New \dots

fortran\@. New \dots

Prof. Stan Lee Djalev

Prof.~Stan Lee Djalev


\section{Cool symbols}
\label{sec:symbols}

\subsection{Need amssymb}

$$
\varnothing  \circledS  \bigstar  \mho  \eth  \cdot
$$

\section{From samples}

\begin{flushright}
\today \\ some text
\end{flushright}
\textbf{From the desk of Prof.~Djalev}

April 7--21 \emph{please} use my
temporary e-mail address:

\begin{center}
\texttt{StanLeeDjalev@dota2.org} \\ some new text % \texttt typewriter font
\end{center}
some newer new text

It is of some concern to me that the terminology used in multi-section math courses is not uniform.
In several sections of the course on matrix theory, the term ``hamiltonian-reduced'' is used.
I, personally, would rather call these ``hyper-simple''. I invite others to comment on this  problem.

\section{Formulae}
In first-year calculus, we define intervals such as $(u, v)$ and $(u, \infty)$.
Such an interval is a \emph{neighborhood} of $a$ if $a$ is in the interval.
Students should realize that $\infty$ is only a symbol, not a number.
This is important since we soon introduce concepts such as $\lim_{x \to \infty} f(x)$.
When we introduce the derivative
\[
\lim_{x \to a} \frac{f(x) - f(a)}{x - a},
\]
we assume that the function is defined and continuous in a neighborhood of $a$.

\[
\left( \frac{1 + x}{2 + y^{2}} \right)^{2}
\]

\begin{align}
\frac{3+x}{5} &= 2 \notag \\
3+x &= 10 \notag \\
x &= 10 - 3 \notag \\
x &= 7 \notag \\
\end{align}

\subsection{Matrix}
\[
\begin{pmatrix}
a + b + c & uv & x - y & 27\\
a + b & u + v & z & 134
\end{pmatrix}
\]

\subsection{Integrals}

$\int_{0}^{\pi} \sin x \, dx = 2$

\subsection{Other}

$F(x_{1}, \dots, x_{n})$ \\
$x_{1} + \dots + x_{n}$ \\
$\varpi = \pi = 3,14 = 3.14 \ne 4.20$ \\
$R^3 \notin R^2$ \\
$\bar M, \overline M, \mathcal{Q}, \mathbb{R}$

\subsection{Arrows}
\begin{enumerate}
\item $\to$ with \verb"\to"
\item $\rightarrow$ with \verb"\rightarrow"
\item $\Rightarrow$ with \verb"\Rightarrow"
\item $\Leftrightarrow$ with \verb"\Leftrightarrow"
\end{enumerate}

\section{Text size}

\begin{tabular}{c|c|c}
\Tiny Tiny  text & \tiny tiny  text & \SMALL SMALL  text  \\\hline
\Small Small  text & \small small  text & \normalsize normalsize  text  \\\hline
\large large  text & \Large Large  text & \LARGE LARGE  text \\\hline
 & \Huge Huge  text & 
\end{tabular}

\end{document}