\documentclass[12pt]{amsart}
\DeclareMathOperator\sign{\mathbf{sgn}} % signum функция
\begin{document}

\section{The building blocks of a formula}

A formula (inline or displayed) is built from components. We group them as follows:
\begin{itemize} % неномериран списък
\item
Arithmetic
\item
Binomial coefficients
\item
Congruences
\item
Delimiters
\item
Ellipses
\item
Integrals
\item
Math accents
\item
Matrices
\item
Operators
\item
Roots
\item
Text
\end{itemize}

In this section, I describe each of these groups, and provide examples illustrating
their use. Read carefully the groups you need!

\begin{description} % описание на нещо
\item[Arithmetic]
We type the arithmetic operations $a + b$, $a-b$, $-a$, $a/b$, and $a$b
in the natural way: \verb"$a + b$", \verb"$a - b$", \verb"$-a$",
\verb"$a / b$", and \verb"$a b$" (the spaces are typed only for readability).

If you wish to use $\cdot$ or $\times$ for multiplication, as in
$a \cdot b$ or $a \times b$, use \verb"\cdot" or \verb"\times", respectively.
The formulas $a \cdot b$ and $a \times b$ are typed as \verb"$a \cdot b$"
and \verb"$a \times b$".

Displayed fractions, such as
\[
\frac{1 + 2x}{x + y + xy}
\]
are typed with \verb"\frac":
\begin{verbatim}
\[
\frac{1 + 2x}{x + y + xy}
\]
\end{verbatim}
\item[Subscripts and superscripts]
Subscripts are typed with \verb"_" and superscripts with \verb"^" (caret).
Subscripts and superscripts should be enclosed in braces, that is, typed
between \verb"{" and \verb"}". To get $a_1$, type \verb"$a_{1}$".
Omitting the braces in this example causes no harm, but to get $a_{10}$,
you must type \verb"$a_{10}$". Indeed, \verb"$a_10$" is typeset as $a_10$.

There is one symbol, the prime (\verb|'|), that is automatically superscripted
in a formula. To get $f'(x)$, just type \verb=$f'(x)$=.
(On many keyboards, the symbol on the key looks like this: \verb"`")

\item[Binomial coefficients]
Binomial coefficients are typeset with the \verb"\binom" command.
\verb"\binom{a}{b + c}" is here inline: $\binom{a}{b + c}$, whereas
\[
\binom{a}{b + c}
\]
is the displayed version.
\item[Congruences]
The two most important forms are
\[
a \equiv v \pmod{\theta}
\quad
\text{typed as }\verb"$a \equiv v \pmod{\theta}$"
\]
\[
a \equiv v \pod{\theta}
\quad
\text{typed as }\verb"$a \equiv v \pod{\theta}$"
\]
\item[Delimiters]
Parentheses and square brackets are examples of delimiters. They are used
to delimit some subformulas, as in \verb"$[(a*b)+(c*d)]^{2}$", which
typesets as $[(a*b)+(c*d)]^{2}$. \LaTeX\ can be instructed to expand them vertically to enclose a formula such as
\[
\left(\frac{1 + x}{2 + y^2}\right)^2
\]
which is typed as
\begin{verbatim}
\[
\left( \frac{1 + x}{2 + y^{2}} \right)^{2}
\]
\end{verbatim}
The \verb"\left(" and \verb"\right)" commands tell \LaTeX\ to size
the parentheses correctly, relative to the size of the formula inside
the parentheses; sometimes the result is pleasing, sometimes not.
\item[Ellipses] % в оригиналния файл беше {Ellipses}, което е грешно!
In a formula, the ellipsis is printed either as \emph{low}
(or \emph{on-the-line}) dots:

$F(x_1,\dots,x_n)$\quad is typed as\qquad \verb"$F(x_{1}, \dots, x_{n})$"

or as centered dots:

$x_1 + \dots + x_n$\quad is typed as\qquad $x_{1} + \dots + x_{n}$

Use \verb"\cdots" and \verb"\ldots" if \verb"\dots" does not work as expected.
\item[Integrals]
The command for an integral is \verb"\int". The lower limit is specified
as a subscript and the upper limit is specified as a superscript.
For example, the formula $\int_{0}^{\pi} \sin x \, dx = 2$ is typed as
\verb"$\int_{0}^{\pi} \sin x \, dx = 2$",
where \verb"\," is a spacing command.

The formula looks bad without the spacing command: \\
$\int_{0}^{\pi} \sin x dx = 2$.
\item[Math accents]
The four most frequently used math accents are:

$\bar{a}$ typed as \verb"$\bar{a}$"

$\hat{a}$ typed as \verb"$\hat{a}$"

$\tilde{a}$ typed as \verb"$\tilde{a}$"

$\vec{a}$ typed as \verb"$\vec{a}$"

\item[Matrices]

Matrix without delimiters:
\[
\begin{matrix}
a + b + c & uv & x - y & 27\\
a + b & u + v & z & 134
\end{matrix}
\]
Matrices with delimiters:
\[
\mathbf{A} =
\begin{pmatrix}
a + b + c & uv\\
a + b & u + v
\end{pmatrix}
\begin{vmatrix}
30 & 7\\
3 & 17
\end{vmatrix}
\begin{bmatrix}
30 & 7\\
3 & 17
\end{bmatrix}
\begin{Vmatrix}
30 & 7\\
3 & 17
\end{Vmatrix}
\]
This is done with \verb"\begin" and then \verb"{pmatrix}",\verb"{vmatrix}",\verb"{bmatrix}" and \verb"{Vmatrix}."
\begin{verbatim}
\[
\mathbf{A} =
\begin{pmatrix}
a + b + c & uv\\
a + b & u + v
\end{pmatrix}
\begin{vmatrix}
30 & 7\\
3 & 17
\end{vmatrix}
\begin{bmatrix}
30 & 7\\
3 & 17
\end{bmatrix}
\begin{Vmatrix}
30 & 7\\
3 & 17
\end{Vmatrix}
\]
\end{verbatim}
% подравняване на уравнения
\item[Cases]
\begin{equation}\label{E:cases}
\sign{(x)} = 
\begin{cases}
-1, &\text{if $x < 0$;}\\
0, &\text{if $x = 0$;}\\
1, &\text{if $x > 0$.}
\end{cases}
\end{equation}
\item[Simple Alignment]
\begin{align}
r^{2} &= s^{2} + t^{2}, \label{E:Pyth}\\
2u + 1 &= v + w^{\alpha}, \label{E:alpha}\\
x &= \frac{y + z}{\sqrt{s + 2u}};\label{E:frac}
\end{align}
\item[Annotated Alignment]
\begin{align}
x &= x \wedge (y \vee z)
&&\text{(by distributivity)}\label{E:DoAlign}\\
&= (x \wedge y) \vee (x \wedge z)
&&\text{(by condition (M))} \notag\\
&= y \vee z. \notag
\end{align}
This one has the equation number on the middle row:
\begin{equation}
\begin{aligned}
x &= x \wedge (y \vee z)
&&\text{(by distributivity)}\label{E:DoAlign2}\\
&= (x \wedge y) \vee (x \wedge z)
&&\text{(by condition (M))}\\
&= y \vee z.
\end{aligned}
\end{equation}
\item[Equations]
Example equation with Integral:
\begin{equation}\label{E:firsteq}
\int_{0}^{\infty} x+1 \, dx
\end{equation}
Reference example: \emph{Check (\ref{E:Pyth}) on page~\pageref{E:Pyth}}
\end{description}
\end{document} 